Object-Oriented Internet - Azure Interoperability

### 2020-12-10 Latex/Manuscript.tex
Final review of the latex text #37
- review and add bibliography

\documentclass{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage[textsize=tiny]{todonotes}

@@

%\listoftodos[TODO list]

@@

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines. For this integration, a new architecture is proposed to support the reactive relationship of communicating parties. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. Prototyping addresses Microsoft Azure Cloud as an example. The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.

@@

The \textbf{field level gateway} is also build atop of the middleware\todo{add ref} concept. The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected. In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.

@@

The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596} \todo{ref to MP, PS gateway implementation}. For this study, prototyping addresses Microsoft Azure cloud products. There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS). Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities. As a result, the platform can be used not only as a cloud-based front-end for CPS. By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process. It is also compliant with the new international standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure are scaled up to millions of users without any additional coding. For the development of the todo front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival. Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS. Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools. Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making. It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.

@@

Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler. It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up. At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services. The transfer process requires data conversion from source to destination encoding. The \emph{IoT\ Hub} is a service hosted in the cloud that supports \emph{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication \todo{Reference}. This communication is transparent, i.e.~it is not data types aware allowing
any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT and HTTPS.

@@

It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts. The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept.

\todo{ cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04} }

\todo{convert textit => emph}

@@

\todo{Overfull}

@@

\bibliography{Manuscript.bib}
\bibliographystyle{aiaa-jacs.bst}

>>>>

\documentclass{article}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{stfloats}
\usepackage{url}
\usepackage{authblk}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{txfonts}
\usepackage{doi}

@@

@@

This article addresses further research on the integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M communication and emerging cloud computing as a \textbf{human-centric} front-end in the context of the Industry 4.0 (I4.0) and Industrial Internet of Things (IIoT) disciplines. For this integration, a new architecture is proposed to support the reactive relationship of communicating parties. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. Prototyping addresses Microsoft Azure Cloud as an example. The proposals are backed by proof of concept reference implementations - the outcome has been just published on GitHub as the open-source (MIT licensed) \cite{OOINetworkingDataRepositoryAzureGateway}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet \cite{RefWorks:doc:5c66740ae4b081adf5804596}.

@@

The \textbf{field level gateway} is also build atop of the middleware\cite{Middleware-Sunyaev} concept. The only difference compared with the \textbf{edge device} is necessity to use officially supported by the cloud vendor services to get connected. In this scenario the process data may be transferred to many clouds at the same time provided that the gateway offers this functionality.

@@

The presented proposals in the article are backed by proof of concept reference implementations\cite{RefWorks:doc:5c66740ae4b081adf5804596}. For this study, prototyping addresses Microsoft Azure cloud products. There are many reasons for selecting Azure to accomplish the cloud-based front-end of Cyber-Physical System (CPS). Azure offers Infrastructure as a Service (IaaS) and Platform as a Service (PaaS) capabilities. As a result, the platform can be used not only as a cloud-based front-end for CPS. By design, the Azure services are compliant with Security Development Lifecycle (SDL) an industry-leading security process. It is also compliant with the new international standard for cloud privacy, namely ISO 27018. Solutions hosted on Azure are scaled up to millions of users without any additional coding. For the development of the CPS front-end, it is essential that Azure provides very efficient storage services usefully for the purpose of real-time process data archival. Azure provides a vast variety of hybrid connections including but not limited to virtual private networks (VPNs), caches, content delivery networks (CDNs), ExpressRoute, and IoT dedicated services that can be directly used to implement cloud-based front-end for CPS. Because it is also integrated with other Microsoft tools like Office 365, Outlook, and SharePoint using Azure allows preserving investment and exporting process data to the mentioned tools. Azure also offers services supporting analytics and intelligence capabilities for further improving business processes and decision making. It is the only cloud platform that offers Blockchain as a Service (BaaS), Machine Learning, Bots, and Cognitive APIs capabilities.

@@

Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler. It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e. protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up. At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services. The transfer process requires data conversion from source to destination encoding. The \textbf{IoT\ Hub} is a service hosted in the cloud that supports \textbf{IoT\ Central} services providing a robust messaging solution - it acts as a central message hub for bi-directional communication \cite{MicrosoftAzureIoTPlatform}. This communication is transparent, i.e.~it is not data types aware allowing any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT, and HTTPS.

@@

It is expected that the functionality implementation expressed by these interfaces is provided as independent external composable parts. The composition is accomplished at run time, and the effective application functionality depends essentially on reusable loosely coupled parts composed applying the dependency injection software engineering and adaptive programming concept \cite{RefWorks:doc:5d9796cbe4b0f66c52dccf04}.

@@

@@

\bibliography{Manuscript.bib}
\bibliographystyle{splncs04} %ieeetr, splncs04
